\chapter*{General Conclusion}
\addcontentsline{toc}{chapter}{General Conclusion} 


\lettrine{A}s it is said, necessity is the mother of invention. In fact, men have devoted themselves through different circumstances into inventing and creating numerous types of accessories and software applications that are beneficial to their own sake. These inventions have always been in pursuance of facilitating and simplifying daily activities.

As for our case, we were interested into expediting and forwarding processes related to fleet management companies. As a matter of fact, we implemented a web component included in an automated fleet dispatching solution. This solution is being improved constantly and our component had its beneficial impact on the user's experience. 
Despite the variety of the clients' preferences, this component proffers generic features that are common to every client. Hence, they are prone to ensure better control and review of their fleet operations.


In addition to that, the new single page application is totally intuitive and easy to use, to the extend of reaching the area of interest of more clients. Being able to observe drivers on the map as well as detecting users' itineraries may turn out to be fruitful as the user is able to keep track of the company's vehicles. But most importantly, he is capable of elaborating statistics concerning the rides booked. Therefore, extensive research in order to deepen the company's knowledge about local citizens' preferences is now attainable. Afterwards, strategic plans are to be put in place straight to prioritize citizens with transportation's high-demand.


As every project can be enhanced and expanded, various perspectives are imminent for our project. We can mention the enhancement of the rides table to the extent of delivering precise required pieces of information.
Moreover, an interesting feature would be to enable the user to leave a comment in the form of a note in order to evaluate the ride, visible by other SaaS offices. 


Last but not least, we may empower our application by automatically generating statistics concerning active zones. The system would be able to recommend certain region in order to increase the number of vehicle bookings.