\chapter*{General Introduction}
\addcontentsline{toc}{chapter}{General Introduction} % to add the intro to the tables of contents



\lettrine[lines=2]{I}n the era of constant evolution, new technologies are being released every day in order to satisfy human being's need for fast and efficient services.

% general needs of security 
%---------The frantic pace at which websites and mobile applications deliver utilities nowadays furthers users' expectations and makes their lives easier.  Nevertheless, it affects users' patience and allows them to become particularly choosy and critical. To the extend of, in several cases, users seeking for reliable services, prefer instant and rapid paid services over slow free ones.
In today's competitive market, responsiveness to customer or supplier demand is often a decisive factor in the success of an organization. The network is considered one of the most critical resources in an organization, both in the private and public sectors.

Connecting your network to the Internet provides access to an enormous amount of information and allows you to share information on an incredible scale. However, the communal nature of the Internet, which creates so many benefits, also offers malicious users easy access to numerous targets. The Internet is only as secure as the networks it connects, so we all have a responsibility to ensure the safety of our networks.

%Especially in daily activities, citizens can not afford to invest a lot of time into transport. Businessmen, daily workers and even tourists have a busy schedule and follow a strict plan. A lot of people arrange a detailed proposal on how to spend the day as they must respect that scheme.   
%---------------------------------
In this context, an automated network security monitoring solution fits as the best option for an organization. The aim of this project is to enable security analysts to monitor network availability, integrity and confidentiality. Detect malicious activity even before it happens.

Our work is presented throughout this report accordingly to the following plan. In the first chapter, we describe the general frame of the project by introducing the host company, going through its main highlights, then presenting the project overview. Throughout the second chapter, we shed the light on some of the most important keywords of our work and provide a brief literature review. Then we study the existing solution, evaluate its efficiency and present our solution. In the third chapter, we make a list of the functional and the non-functional requirements related to our application. In addition, we present several use case diagrams to clarify the features of our solution. In the fourth chapter, we describe the application's architecture and its design. In the fifth chapter, we detail the description of the different technologies used to build the project and present the main interfaces using screen-shots.

Finally, we conclude our work by giving future prospects and potentials upgrades for our application.
\thispagestyle{empty}